A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 methodology.tex
bad break

In our example, we add a \verb+&+ borrow operator to the variable \verb+tail+, which gives rise to an ASTDiff path introducing a new parent node (\verb+ExprReference+) for \verb+tail+. We also add a \verb+clone()+ method call. This addition gives rise to two ASTDiff paths: one indicating that the \verb+head+ node is now part of a \verb+ExprMethodCall+, and one indicating the new sibling node for \verb+head+ representing the \verb+clone()+. (Among the terminals, we only keep \verb+clone+ in our paths, as it is a BC-related keyword.) One path for the \verb+&+ borrow operator and two for the call to \verb+clone()+ result in three paths in the ASTDiff, even if it only looks like we had made two modifications.

>>>>

In our example, we add a \verb+&+ borrow operator to the variable \verb+tail+, which gives rise to an ASTDiff path introducing a new parent node (\verb+ExprReference+) for \verb+tail+. We also add a call to \verb+clone()+. This addition gives rise to two ASTDiff paths: one showing that the \verb+head+ node now belongs to an \verb+ExprMethodCall+, and one indicating the new sibling node for \verb+head+ representing the \verb+clone()+. (Among the terminals, we only keep \verb+clone+ in our paths, as it is a BC-related keyword.) One path for the \verb+&+ borrow operator and two for the call to \verb+clone()+ result in three paths in the ASTDiff, even if it only looks like we had made two modifications.
